### 2015-02-16 docs/report/intro.tex

The goal of this professional assignment is to provide an alternative for parallel code eection in EcmaScript, through a library that exposes high order functions to model algorithmic skeletons such as map, filter and reduce. This library will take advantage of Web Workers \cite{w3c-ww} (the mechanism proposed by browsers for parallelism at the time of writing) to allow the simultaneous execution of code in multiple processors.

>>>>

The goal of this professional assignment is to provide an alternative for parallel code execution in EcmaScript, through a library that exposes high order functions to model algorithmic skeletons such as map, filter and reduce. This library will take advantage of Web Workers \cite{w3c-ww} (the mechanism proposed by browsers for parallelism at the time of writing) to allow the simultaneous execution of code in multiple processors.

### 2015-02-16 docs/report/serialization_transference.tex
Array sharing documentation

\section{Serialization and Transference}

@@

Nevertheless, there are additional time consuming tasks other than the main computation that need to be considered when performing the operation in parallel in programs with no shared memory. These are:
\begin{itemize}
  \item Partitioning or joining the elements to transfer.
  \item Serializing/deserializing the elements to transfer.
  \item Transferring the elements between the main thread and the workers.
\end{itemize}

All of the above happens twice, once when starting the computation and once when it ends, since the resulting need to be put together.

@@

As the aforementioned interface states one can either send just a message or send a message with a sequence of transferable objects. From section \textbf{2.7.5} of the HTML Standard \cite{html-whatwg}:
\textit{"Some objects support being copied and closed in one operation. This is called transferring the object, and is used in particular to transfer ownership of unsharable or expensive resources across worker boundaries."}

Considering the definition of a \code{Transferable} the latter seems like a good alternative to minimize both \(T_{s}\) and \(T_{s}\). Even more so when one considers that otherwise objects are copied using structured cloning(explained in section \textbf{2.7.5} of that same standard).

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \code{postMessage} with and without structured cloning for a \ttarray{}. Both transfer a \ttarray{} back and forth between the UI thread and a worker; the only difference between the two is that one has 100000 elements in the \ttarray{} and the other one 1000000.

@@

\subsubsection{Conclusion}
As we can see from the previous results increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \code{Transferable} objects, it scales. On the other hand, the amount of operations that can be performed with structure cloning greatly decreases.

>>>>

\section{Serialization and Transference}
\label{sec:serialization-and-transference}

@@

Nevertheless, there are additional time consuming tasks other than the main computation that need to be considered when performing the operation in parallel in programs with no shared memory. These are:
\begin{itemize}
  \item Partitioning or joining the elements to transfer.
  \item Serializing/deserializing the elements to transfer.
  \item Transferring the elements back and forth between the main thread and the workers.
\end{itemize}

All of the above happens twice, once when starting the computation and once when it ends, since the result from each worker needs to be consolidated before returning the new array with the transformed elements.

@@

As the aforementioned interface states one can either send just a message or send a message with a sequence of transferable objects. From section \textbf{2.7.5} of the HTML Standard \cite{html-whatwg}:
\textit{``Some objects support being copied and closed in one operation. This is called transferring the object, and is used in particular to transfer ownership of unsharable or expensive resources across worker boundaries."}

Considering the definition of a \code{Transferable} the latter seems like a good alternative to minimize both \(T_{s}\) and \(T_{s}\). Even more so when one considers that otherwise objects are copied using structured cloning(explained in section \textbf{2.7.6} of that same standard).

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \code{postMessage} with and without structured cloning for a \ttarray{}. Both transfer a \ttarray{} back and forth between the UI thread and a worker; the only difference between the two is that one has 100000 (a hundred thousand) elements in the \ttarray{} and the other one 1000000 (a million).

@@

\subsubsection{Conclusion}
As we can see from the previous results increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \code{Transferable} objects, it scales. On the other hand, the amount of operations that can be performed with structured cloning greatly decreases.
